Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-01-29 paper.tex
update

\section{Comprehensive Quality-Aware Service model}\label{qswsc_approach}
In this section, we propose a comprehensive quality-aware service model to achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS for semantic web service composition.

@@

\subsection{Comprehensive Quality-Aware Model}\label{qualityModel}
In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition. This model overcome the disadvantages of current prevailing QoS-aware optimisation that ignores quality of semantic matchmaking.

\textbf{Semantic Web Service link}
\textbf{Semantic matchmaking model}. Due to the discretisational characteristics of different match types and values assigned to matching types that driven by the cost of data integration and manipulation \cite{lecue2009optimizing}, partial ordering match types are considered to be one factor for the semantic matchmaking quality. For example, Exact matching type demands less time for computation compared to that of Plugin match. Another factor in our proposed model is concept similarity, which could be evaluated based on the edge counting method defined in \cite{shet2012new}. This formula (\ref{equation1}) is used to estimate the similarity between concept-related parameters for selecting web services. Therefore, given the quality match type and the concept similarity of two parameters-related concepts, the semantic matchmaking quality of matched parameters is defined by Formula (\ref{equation2}), where the value of $q(p_ {mt})$ follows the same settings in \cite{lecue2009optimizing}. Particularly, 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).

@@

\begin{equation}
\label{equation2}
q(p_{sm}) \stackrel{.}{=} (q(p_ {mt}), \  q(p_ {s}))
\end{equation}

Further more, edges represent services connections in our weighted graph representations, where assigned weight value $q(e_{sm})$ is considered to be semantic matching quality on edge level according to parameter aggregations. The weight value $q(e_{sm})$ is defined in \ref{equation3}, where $q(e_ {mt})$ and $q(e_ {s})$ are the average value of concept-related parameters quality in $q(p_{mt})$ and $q(p_{s})$ respectively.

\begin{equation}
\label{equation3}
q(e_{sm}) \stackrel{.}{=} (q(e_ {mt}), \  q(e_ {s}))
\end{equation}

\textbf{Comprehensive quality model}. Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional requirements. The comprehensive quality of our service composition representation refers to QoS of service vertices and Semantic matching quality of Edges in weighted graphs. Consequently, the comprehensive quality model is defined in Formula (\ref{equation4}), which could be further broken down into Formula (\ref{equation5}). 
\begin{equation}
\label{equation4}
q_{cq} \stackrel{.}{=} (q(e_ {sm}), \  q(v_ {QoS}))
\end{equation}
\begin{equation}
\label{equation5}
q_{cq} \stackrel{.}{=} (q(e_ {mt}), \  q(e_ {s}), \  q(v_{a}),\  q(v_{r}),\  q(v_{c}),\  q(v_{t}))
\end{equation}

\textbf{Quality aggregate matrix}. The quality aggregation is defined based on the constructs of composition web services, in consideration of functional and non-functional properties. The quality on construct level is further calculated by following the rules summarised in Table \ref{table1}.

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\centering
\caption{Quality aggregate matrix for semantic web service composition}
\label{table1}
\begin{tabular}{c|c|c|c|c}
\hline
\multicolumn{3}{c|}{Composition Construct}                                      & Sequence                             & Parallel \\ \hline
\multirow{5}{*}{Quality} & \multirow{2}{*}{F}    & $Q(e_ {mt})$  &$\prod_{n=1}^{m} q(e_ {mt})$          &  $\prod_{n=1}^{m} q(e_ {mt})$ \\ \cline{3-5}
                                &                                & $Q(e_ {s})$  & $(\sum_{n=1}^m q(e_ {s}))/m$        &  $(\sum_{n=1}^m q(e_ {s}))/m$  \\ \cline{2-5}   
                                & \multirow{4}{*}{NF} & $Q(v_{a})$    & $\prod_{n=1}^{m} q(v_a)$             &  $\prod_{n=1}^{m} q(v_a)$ \\ \cline{3-5} 
                                &                                & $Q(v_{r})$    & $\prod_{n=1}^{m} q(v_r)$             &  $\prod_{n=1}^{m} q(v_r)$ \\ \cline{3-5} 
                                &                                & $Q(v_{c})$    & $\sum_{n=1}^m q(v_ {c})$             &  $\sum_{n=1}^m q(v_ {c})$ \\ \cline{3-5} 
                                &                                & $Q(v_{t})$    & $\sum_{n=1}^m q(v_ {t})$             &  $max(q(v_ {t}))$ \\ \hline
\end{tabular}
\end{table}

\subsection{Objective Function}
In real life, given a unique and optimised solution is always easier for customers to pick up directly when many quality criteria involved into decision making, rather than provided a set of solutions. Therefore, it is very practical to define a single fitness as a weighted sum of all the quality related components in Formula (\ref{equation6}), where weights setting is very flexible, it could be adjusted according to users' preferences. The fitness value of 1 means the best comprehensive quality and 0 means the worst. For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the fitness value falls within the range from 0 to 1. Therefore, the service composition problem in this paper is treated as a fitness maximisation problem.
\vspace{-0.2cm}
\begin{equation}
\label{equation6}
Fitness = w_1 \hat{MT} + w_2 \hat{S} + w_3 \hat{A} + w_4 \hat{R} + w_5(1 - \hat{T}) + w_6(1 - \hat{C})
\end{equation}
\noindent where $\sum_{i=1}^{6} w_i = 1$
\\
\vspace{-0.2cm}
\begin{equation}
\label{equation7}
\hat{Q_k} = 
\begin{cases}
	\frac{Q_k - Q_{k, min}}{Q_{k, max} - Q_{k, min}} & \text{ if }Q_{k, max} - Q_{k, min} \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\noindent where $k$ $=$ $1$, $2$, $3$, and $4$, where $Q_1$ as $MT$, $Q_2$ as $S$, $Q_3$ as $A$, and $Q_4$ as $R$.
\begin{equation}
\label{equation8}
\hat{Q_j} = 
\begin{cases}
	\frac{Q_{j,max} - Q_j}{Q_{j, max} - Q_{j, min}} & \text{ if }Q_{j, max} - Q_{j, min} \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\noindent where $j$ $=$ $1$, and $2$, where $Q_1$ as $T$ and $Q_2$ as $C$.

\section{PSO-based Appraoch to QoS-Aware Semantic Web Service Composition}\label{qswsc_approach}

\begin{figure*}[h]
\centering
\fbox{\includegraphics[scale=.4]{overview.pdf}}
 \caption{Overview of POS-based automated semantic web service composition approach.}
 \label{overview}
\end{figure*}

@@

\subsection{Composition Weighted Graph}
We defined our semantic web service composition solution as a weighted graph $WG = (V, E)$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of edges $E = {e_{1}, e_{2},... e_{n}}$. Each $e$ is associated with $q(e_{sm})$ as weight value that mapped to a pair of quality values $q(e_{mt})$ and $q(e_{s})$ on the edge level, and $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$. Here we provide an example of the web service composition, which is described in Fig. \ref{wscs}. The data of composition web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},... e_{n}}$ assigned as weights.

>>>>

\section{Comprehensive Quality Model}\label{qswsc_approach}
In this section, we propose a comprehensive quality-aware service model to achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS for semantic web service composition.

@@

\subsection{Comprehensive Quality Model}\label{qualityModel}
In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition. This model overcome the disadvantages of current prevailing QoS-aware optimisation that ignores quality of semantic matchmaking.

\textbf{Semantic web Service link}. In Fig. \ref{semanticLink}, $S_{1}$ and $S_{2}$ are linked to together if exists any parameter matchmaking between  Output of $S_1$ and Input of $S_2$.  Therefore, measuring semantic matchmaking quality ($SM$) is to measure the quality of semantic web service link ($sm_{L}$), which is aggregated from the quality of parameter matchmaking ($sm_{P}$). This semantic web service link is adopt from \cite{lecue2009optimizing}.

\begin{figure}[h]
\centering
\fbox{\includegraphics[scale=.38]{semanticLink.pdf}}
 \caption{ An example of semantic web service link}
 \label{semanticLink}
\end{figure}

\textbf{Semantic web service link quality model}. Due to the discretisational characteristics of different match types and values assigned to matching types that driven by the cost of data integration and manipulation \cite{lecue2009optimizing}, partial ordering match types are considered to be one factor for quality of parameter matchmaking, denoted as $mt_{p}$,  For example, Exact matching type demands less time for computation compared to that of Plugin match. Another factor in our proposed model is concept similarity, which could be evaluated based on the edge counting method defined in \cite{shet2012new}. This formula (\ref{equation1}) is used to estimate the concept similarity between matching parameters, which is denoted as $s_{p}$. Therefore, given the quality of parameter matchmaking type and quality of parameter concept similarity, the quality of parameter matchmaking is defined by Formula (\ref{equation2}), where the value of $mt_{p}$ follows the same settings in \cite{lecue2009optimizing}. Particularly, 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).

@@

\begin{equation}
\label{equation2}
sm_{p} \stackrel{.}{=} (mt_ {p}, \  s_ {p})
\end{equation}

Further more, semantic web service link represent services connections, where quality of semantic web service link $sm_{L})$ is considered to be semantic matching quality on service connection level by parameter aggregations. Therefore, $sm_{L}$ is defined in formula (\ref{equation3}), where $sm_{L}$ and $s_{L}$ are the average value of concept-related parameters quality in $mt_{P}$ and $s_{P}$ respectively.

\begin{equation}
\label{equation3}
sm_{L} \stackrel{.}{=} (mt_ {L}, \  s_ {L})
\end{equation}

\textbf{Comprehensive quality model}. The comprehensive quality model consider both semantic matchmaking quality and QoS. The semantic matchmaking quality refers to the quality of semantic web service link. Consequently, the comprehensive quality model is defined in Formula (\ref{equation4}), which could be further broken down into Formula (\ref{equation5}). 
\begin{equation}
\label{equation4}
q_{cq} \stackrel{.}{=} (sm_ {L}, \  QoS_ {s})
\end{equation}
\begin{equation}
\label{equation5}
q_{cq} \stackrel{.}{=} (mt_ {L}, \  s_ {L}, \  a_{s},\  r_{s},\  c_{s},\  t_{s})
\end{equation}

\textbf{Semantic matchmaking quality aggregation}. The quality aggregation is defined based on the constructs of composition web services, in consideration of quality semantic web service link and QoS. The quality on composition solution is further calculated by following the formula (\ref{equation6})(\ref{equation7}), and QoS aggregation are discussed in Sect. \ref{Quality of Service and Composition Constructs}

\begin{equation}
\label{equation6}
MT {=} \prod_{n=1}^{m} mt_ {L_{n}}
\end{equation}
\begin{equation}
\label{equation7}
S {=} (\sum_{n=1}^m s_ {L_{n}})/m
\end{equation}

\subsection{Objective Function}
In real life, given a unique and optimised solution is always easier for customers to pick up directly when many quality criteria involved into decision making, rather than provided a set of solutions. It is very practical to define a single fitness as a weighted sum of all the quality related components in Formula (\ref{equation8}). Note that weights can be adjusted according to users' preferences. The function value of 1 means the best comprehensive quality and 0 means the worst. For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the function value falls within the range from 0 to 1. Therefore, the service composition is try to maximise the value of objective function.
\vspace{-0.2cm}
\begin{equation}
\label{equation8}
Fitness = w_1 \hat{MT} + w_2 \hat{S} + w_3 \hat{A} + w_4 \hat{R} + w_5(1 - \hat{T}) + w_6(1 - \hat{C})
\end{equation}
\noindent where $\sum_{i=1}^{6} w_i = 1$
\\
\vspace{-0.2cm}
\begin{equation}
\label{equation9}
\hat{Q_k} = 
\begin{cases}
	\frac{Q_k - Q_{k, min}}{Q_{k, max} - Q_{k, min}} & \text{ if }Q_{k, max} - Q_{k, min} \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\noindent where $k$ $=$ $1$, $2$, $3$, and $4$, where $Q_1$ as $MT$, $Q_2$ as $S$, $Q_3$ as $A$, and $Q_4$ as $R$.
\begin{equation}
\label{equation10}
\hat{Q_j} = 
\begin{cases}
	\frac{Q_{j,max} - Q_j}{Q_{j, max} - Q_{j, min}} & \text{ if }Q_{j, max} - Q_{j, min} \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\noindent where $j$ $=$ $1$, and $2$, where $Q_1$ as $T$ and $Q_2$ as $C$.

\section{PSO-based Approach to QoS-Aware Semantic Web Service Composition}\label{qswsc_approach}

\begin{figure*}[h]
\centering
\fbox{\includegraphics[scale=.4]{overview.pdf}}
 \caption{Overview of POS-based approach to QoS-aware automated semantic web service composition.}
 \label{overview}
\end{figure*}

\subsection{Weighted Graph Composition}

We defined our semantic web service composition solution as a weighted graph $WG = (V, E)$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of edges $E = {e_{1}, e_{2},... e_{n}}$. Each $e$ is associated with $q(e_{sm})$ as weight value that mapped to a pair of quality values $q(e_{mt})$ and $q(e_{s})$ on the edge level, and $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$. Here we provide an example of the web service composition, which is described in Fig. \ref{wscs}. The data of composition web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},... e_{n}}$ assigned as weights.

\subsection{PSO-based Approach to QoS-Aware Semantic Web Service Composition}

@@
